Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-01 analysis/paper/paper.Rmd
Move library loading to later in doc

```{r, setup, echo = FALSE, message=FALSE}
library("Reproducibility.in.Plant.Pathology")

packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "egg",
  "english",
  "extrafont",
  "flextable",
  "ggplot2",
  "ggpubr",
  "here",
  "janitor",
  "knitr",
  "officer",
  "patchwork",
  "rsvg",
  "tidyr",
  "tools"
)

@@

>>>>

```{r, setup, echo = FALSE, message=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "egg",
  "english",
  "extrafont",
  "flextable",
  "ggplot2",
  "ggpubr",
  "here",
  "janitor",
  "knitr",
  "officer",
  "patchwork",
  "rsvg",
  "tidyr",
  "tools"
)

@@

library("Reproducibility.in.Plant.Pathology")
